Competing Bandits: \\ The Perils of Exploration under Competition

### 2020-06-30 journal paper/content/sec-intro.tex
Started going through the intro.

Learning from interactions with users is ubiquitous in modern customer-facing systems, from product recommendations to web search to content selection to fine-tuning user interfaces. These interactions are essential for the development of high quality products, but, in order to learn what products are high quality, firms need to implement systems that engage in \emph{exploration}: deploying potentially suboptimal products in order to acquire new information to make more informed product decisions tomorrow.

In this paper, we initiate a study of the interplay between \exploration and \competition. The fundamental tension is that while exploration allows for the deployment of high quality products in the long-run, it leads to poor user experiences in the short-run. Exploration can therefore harm the perception users have of a system, which may lead them to instead utilize a competing system. This would leave the system with lower market share and therefore less users to learn from relative to its competitors and allow its competitors to make further progress on their learning problem. Users therefore serve three distinct roles: they are customers that generate revenue, they are sources of data for learning, and they are self-interested agents who choose among the competing systems.

>>>>

Learning from interactions with users is ubiquitous in modern customer-facing systems, from product recommendations to web search to content selection to fine-tuning user interfaces. Many systems purposefully implement \emph{exploration}: making potentially suboptimal choices for the sake of acquiring new information.
Online platforms routinely deploy A/B tests, and are increasingly adopting  more sophisticated exploration methodologies based on \emph{multi-armed bandits}, a well-known framework for exploration and making decisions under uncertainty.

%~\cite{KohaviAB-2015,KohaviLSH09}

In this paper, we initiate a study of the interplay between \exploration and \competition. Systems that engage in exploration typically need to compete against one another; most importantly, they compete for users. This creates a tension:
%between \exploration and \competition. 
while exploration may be essential for improving the service tomorrow, it may degrade quality and make users leave \emph{today}, in which case there will be less users to learn from. This may further degrade the platform's performance relative to competitors who keep learning and improving from \emph{their} users, and so forth. Taken to the extreme, such dynamics may create a ``death spiral" effect when the vast majority of customers eventually switch to competitors. Users therefore serve three distinct roles: they are customers that generate revenue, they are sources of data for learning, and they are self-interested agents who choose among the competing systems.

\ascomment{stopped here.}
